An exposition on the propriety of restricted Boltzmann machines

### 2016-09-12 writing/draft.Rmd
fix some latex table crap

cbind(tbl[1:8,], tbl[9:16,], tbl[17:24,]) %>%
  kable(caption = "\\label{tab:theta}Parameters used to fit a test case with $V = H = 4$. This parameter vector was chosen as a sampled value of $\\boldsymbol \\theta$ that was not near the convex hull of the sufficient statistics for a grid point in figure \\ref{fig:degen_plots} with $< 5%$ near-degeneracy.")
```

We considered a test case with $V = H = 4$ and parameters given in table \ref{tab:theta}. This parameter vector was chosen as a sampled value of $\\boldsymbol \\theta$ that was not near the convex hull of the sufficient statistics for a grid point in figure \\ref{fig:degen_plots} with $< 5%$ near-degeneracy. We simulated $n = 5,000$ as a training set and fit the RBM using three Bayes methodologies. These involved the following:

@@

\begin{table}[ht]
\centering
\begin{tabular}{|l|c|c|}
\hline 
Method & Hyperparameter & Value \\ 
\hline \hline
\multirow{2}{*}{Trick Prior} & $C_1$ & $\frac{C}{N}\frac{1}{H + V}$ \\
 & $C_2$ & $\frac{C}{N}\frac{1}{H*V}$ \\
\hline
\multirow{2}{*}{Truncated Normal} & $\sigma^2_{main}$ & $\frac{1}{H + V}$ \\
 & $\sigma^2_{interaction}$ & $\frac{1}{H*V}$ \\
\hline
\multirow{2}{*}{Marginalized Likelihood} & $\sigma^2_{main}$ & $\frac{1}{H + V}$ \\
 & $\sigma^2_{interaction}$ & $\frac{1}{H*V}$ \\
\hline
\end{tabular}
\caption{The values used for the hyperparameters for all three fitting methods. A rule of thumb is imposed which decreases prior variances for the model parameters as the size of the model increases and also shrinks $\boldsymbol \theta_{interaction}$ more than $\boldsymbol \theta_{main}$.}
\label{tab:hyperparam}
\end{table}

>>>>

cbind(tbl[1:8,], tbl[9:16,], tbl[17:24,]) %>%
  kable(caption = "\\label{tab:theta}Parameters used to fit a test case with $V = H = 4$. This parameter vector was chosen as a sampled value of $\\boldsymbol \\theta$ that was not near the convex hull of the sufficient statistics for a grid point in figure \\ref{fig:degen_plots} with $< 5$\\% near-degeneracy.")
```

We considered a test case with $V = H = 4$ and parameters given in table \ref{tab:theta}. This parameter vector was chosen as a sampled value of $\boldsymbol \theta$ that was not near the convex hull of the sufficient statistics for a grid point in figure \ref{fig:degen_plots} with $< 5$\% near-degeneracy. We simulated $n = 5,000$ as a training set and fit the RBM using three Bayes methodologies. These involved the following:

@@

\begin{table}[ht]
\centering
\caption{The values used for the hyperparameters for all three fitting methods. A rule of thumb is imposed which decreases prior variances for the model parameters as the size of the model increases and also shrinks $\boldsymbol \theta_{interaction}$ more than $\boldsymbol \theta_{main}$.}
\label{tab:hyperparam}
\begin{tabular}{|l|c|c|}
\hline 
Method & Hyperparameter & Value \\ 
\hline \hline
\multirow{2}{*}{Trick Prior} & $C_1$ & $\frac{C}{N}\frac{1}{H + V}$ \\
 & $C_2$ & $\frac{C}{N}\frac{1}{H*V}$ \\
\hline
\multirow{2}{*}{Truncated Normal} & $\sigma^2_{main}$ & $\frac{1}{H + V}$ \\
 & $\sigma^2_{interaction}$ & $\frac{1}{H*V}$ \\
\hline
\multirow{2}{*}{Marginalized Likelihood} & $\sigma^2_{main}$ & $\frac{1}{H + V}$ \\
 & $\sigma^2_{interaction}$ & $\frac{1}{H*V}$ \\
\hline
\end{tabular}
\end{table}
